Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary

### 2023-11-05 manu-draft.qmd
pinco mod scratch

Additional models were constructed for the FIM and PDEM datasets to evaluate seagrass change relative to temperature and salinity. These models did not include stressor metrics, but rather used direct measurements of salinity and temperature as independent variables. Models of temperature or salinity to predict daily measurements are not possible with the FIM and PDEM monitoring designs because random locations were used for each sample date. However, the sample sizes for the FIM and PDEM models were much larger than those for the EPC data, where the latter was limited by the annual timestep of the transect surveys. This allowed for more flexible models that are less limited by degrees of freedom. GAMs were used to evaluate seagrass percent cover for the FIM data using continuous temperature and salinity as independent variables. Interactions with factor variables for bay segment and time period as above were also included. The GAMs also evaluated interactions between salinity and temperature to determine if both factors had an additive effect on seagrass change. The GAMs for the PDEM data were constructed similarly, except only Old Tampa Bay was evaluated (no bay segment interaction) and the seagrass response variable was presence/absence (i.e., a binomial distribution was used).

>>>>

Additional models were constructed for the FIM and PDEM datasets to evaluate seagrass change relative to temperature and salinity. These models did not include stressor metrics, but rather used direct measurements of salinity and temperature as independent variables. Models of temperature or salinity to predict daily measurements were not possible with the FIM and PDEM monitoring designs because random locations were used for each sample date. However, the sample sizes for the FIM and PDEM models were much larger than those for the EPC data, where the latter was limited by the annual timestep of the transect surveys. This allowed for more flexible models that are less limited by degrees of freedom. GAMs were used to evaluate seagrass percent cover for the FIM data using continuous temperature and salinity as independent variables. Interactions with factor variables for bay segment and time period as above were also included. The GAMs also evaluated interactions between salinity and temperature to determine if both factors had an additive effect on seagrass change. The GAMs for the PDEM data were constructed similarly, except only Old Tampa Bay was evaluated (no bay segment interaction) and the seagrass response variable was presence/absence (i.e., a binomial distribution was used).
